\addcontentsline{toc}{chapter}{References}

\begin{thebibliography}{4}
\bibitem{graham} Alejo Hausner, CS Department, Princeton University
 \emph{http://www.cs.princeton.edu/courses/archive/spr10/cos226/demo/ah/GrahamScan.html (2011).} Prentice Hall
 
\bibitem{hadamard} Teknomo K. Hadamard Product. 2011. Available from \url{http://people.revoledu.com/kardi/tutorial/LinearAlgebra/HadamardProduct.html} 

\bibitem{bresenham} Flanagan C. The Bresenham Line-Drawing Algorithm. 2011. Available from \url{http://www.cs.helsinki.fi/group/goa/mallinnus/lines/bresenh.html} 

\bibitem{normal-dist} Inductiveload. Normal Distribution: curve. 2008. Available from \url{http://en.wikipedia.org/wiki/File:Normal_Distribution_PDF.svg} 
\bibitem{length-parameter} Wallach H. M. Introduction to Gaussian Process Regression: curve. 2005. Available from \url{http://www.cs.umass.edu/~wallach/talks/gp_intro.pdf} 

\bibitem{simple-covariance} Ebden M. Gaussian Processes for Regression: A Quick Introduction. aug 2008. Available from \url{http://www.robots.ox.ac.uk/~mebden/reports/GPtutorial.pdf} 


\bibitem{intro-to-gpr} Wallach H. M. Introduction to Gaussian Process Regression. jan 25, 2005. Available from \url{http://www.cs.umass.edu/~wallach/talks/gp_intro.pdf} 

\bibitem{fire-tirangleimage} Wikipedia,       \url{http://upload.wikimedia.org/wikipedia/commons/2/20/Fire_triangle.svg}, des 13, 2011

\bibitem{irevol} Patrick Meier, \underline{iRevolution} \url{http://irevolution.net/2011/01/20/what-is-crisis-mapping/} Posted on:jan 20, 2011, Visited on: des 14, 2011

\bibitem{mobsurv} Nicholas D. Lane, Emiliano Miluzzo, Hong Lu, Daniel Peebles, Tanzeem Choudhury,
and Andrew T. Campbell, Dartmouth College, \underline{IEEE Communications Magazine} \url{http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=5560598 } Release: September 2010, Visited on: des 14, 2011

\bibitem{filmcrisis} Alison Stewart, "Need to Know", \underline{Crisis Mapping}, Premier date: may 13, 2011, \url{http://gis-techniques.blogspot.com/2011/05/new-way-of-mapping-crisis-mapping.html}

\bibitem{usha} "Ushahidi" \url{http://www.ushahidi.com/About-us} Visited on: des 14, 2011

\bibitem{springlink} Iizuka K ,Iizuka Y,Yoshida K, \emph{A Real-time Disaster Situation Mapping System for University Campuses}, \url{http://www.springerlink.com/content/0302-9743/?k=crisis+mapping} Publish date: 2011 Visited on: des 15, 2011

\bibitem{gitvers} "Version control glossary", \underline{What is version control} \url{What is version control} Visited on: des 14, 2011

\bibitem{gitis} "git the fast vesion control system", \underline{Git is...} \url{http://git-scm.com/}, Visited on: des 14, 2011

\bibitem{gausreg} Ebden M. \underline{Gaussian Processes for Regression: A Quick Introduction} Publish date: August 2008, \url{http://www.robots.ox.ac.uk/~mebden/reports/GPtutorial.pdf}, Visited on: des 15, 2011

\bibitem{intgausreg} Wallach H. M. \underline{Introduction to Gaussian Process Regression}
Publish date: January 25,2005
\url{http://www.cs.umass.edu/~wallach/talks/gp_intro.pdf}, Visited on: des 15, 2011

\bibitem{firebev} "Fire ecology and management", \underline{Fire Behaviour}, \url{http://learnline.cdu.edu.au/units/sbi263/fundamentals/behaviour.html}
Visited on: des 14, 2011, Last modified: aug 09, 2005

\bibitem{firebas} "Natural Resources Canada", \underline{Fire Basics}, \url{http://fire.cfs.nrcan.gc.ca/questions-fire-feu-eng.php} Visited on: des 14, 2011
Last modified: jun 30, 2011

\bibitem{rateofspread} "Knowledge and Application", \underline{Rate of Spread}, \url{http://www.forestencyclopedia.net/p/p478} Visited on: des 14, 2011, Last modified: nov 14, 2008

\bibitem{wildfire} Stephen J. Pyne, Patricia L. Andrews, Richard D. Laven, \emph{Introduction to Wildland fire. 2nd ed.}, John Wiley and Sons. Inc. 1996: p.37
\url{http://books.google.no/books?id=yT6bzpUyFIwC&pg=PA37&dq=Rothermel%E2%80%99s+equation+have+been+the+basis+for+most+of+the+fire+spread+prediction+models&hl=en&ei=j-foTsi9Esj34QSIof33CA&sa=X&oi=book_result&ct=result&redir_esc=y#v=onepage&q=Rothermel%E2%80%99s%20equation%20have%20been%20the%20basis%20for%20most%20of%20the%20fire%20spread%20prediction%20models&f=false}

\bibitem{firemov} "Fire ecology and management in northern Australia", \underline{Topography}, \url{http://learnline.cdu.edu.au/units/sbi263/fundamentals/topography.html}, 
Visited on: des 15, 2011

\bibitem{fireslope} "Unit2: Topographic Influences on Wildland Fire Behavioir" \url{http://deved.meted.ucar.edu/fire/s290/unit2/media/graphics/slopeandfirebehav.jpg} Visited on: des 15, 2011

\bibitem{firetypeimage} "Fire ecology and management in northern Australia", \underline{Fire regime}, \url{http://learnline.cdu.edu.au/units/sbi263/fundamentals/regime.html}, Visited on: des 15, 2011

\bibitem{firetypeimage} "Fire ecology and management in northern Australia", \underline{Climate, vegetation and fire}, \url{http://learnline.cdu.edu.au/units/sbi263/ecology/climate.html}, Visited on: des 15, 2011

\bibitem{fireweather} "Fire ecology and management in northern Australia", \underline{Fire weather}, \url{http://learnline.cdu.edu.au/units/sbi263/fundamentals/weather.html}, Visited on: des 15, 2011

\bibitem{relvhum} National Wildlife Coordinating Group, \emph{FIRE EFFECTS GUIDE
}, \url{http://www.nwcg.gov/pms/RxFire/FEG.pdf}, Last modified: jun 21, 2001, Visited on: des 15, 2011. 

\end{thebibliography}
