\section{Requirements}
In this project it was necessary to create a system which would receive raw data from sensors, interpret the data and visualise the findings on a map. The project had a heavy emphasis on certain non-functional requirements inherent in the problem and some were simply not included as they did not fall within the project problem domain. The project problem domain being the crisis map, and the non-functional requirements that were not included were related to the sensors. The reason for this prioritization was that the limitations in the current generation of smart phones, as discussed in the literature review, made some requirements impossible to complete. Smart phones were not equipped with smoke detectors and the power consumption of the application would drain the battery too quickly. Furthermore new and better hardware for smart phones was expected to be released. As such this project was based on the assumption that precises sensors and batteries with a longer life expectancy would be released, making it unnecessary to limit the project by accounting for current limitations.
\\\\
The non-functional requirements consists of the environmental simulation and the Gaussian processes. The simulation were to simulate an actual crisis situation by starting the forest fire and placing sensors on the simulation map. This map would not be visible to the user and function merely as a way to estimate the accuracy of the interpreter. The Gaussian processes were to receive data from the simulated sensors and output predictions indicating where the fire is and where it will be.
\\\\
The functional requirements consists of the Crisis Map. The map function as both a visual representation of the predicted data and as a method of measuring the accuracy of the system. By comparing the simulated map and the predicted map one would obtain the accuracy of the system. The accuracy is naturally required to be fairly high as incorrect predictions could cost lives and resources if the system were to be deployed in a real crisis situation.